Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
more fixes

Model-based diagnosis is a well-known approach that has been proposed by the
DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,Mayer:2008:EMM:1642931.1642950}.

@@

We used subject programs from the \dfj{}
benchmark~\cite{just-defects4j-issta2014} in our evaluation.
Table~\ref{tab:df4j} shows size, number of tests, and number of
faults, for each considered program.

@@

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\Fix{cite}. A fault of omission occurs when
\Fix{...explain...}. Intuitivelly, the ability of techniques to
produce good diagnosis in those cases reduce as \Fix{...explain...}. A
total of $59.7\%$ of the cases in this dataset manifest fault of
omission, which is a good indication of difficulty.

@@

\Mar{incorporate this here. we were presenting this too early (initial
  par. of results). not very appealing ;)}
\Fix{
The remaining faults were not considered because
(1) faults belong to the \closure{} project which requires high CPU to perform
the \combpar{k} evaluation  or (2) faults whose test outputs were not
reproducible in the machine used to run the experiments.
}

%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.

>>>>

Model-based diagnosis is a well-known approach that has been proposed by the
DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.
\Sof{A primeira citação estava repetida. @Rui, por favor, verifica se a segunda é a que eu introduzi
mayer2008prioritising ou se é outra ou então se estava repetida por engano.}

@@

We used subject programs from the \dfj{}
benchmark~\cite{just-defects4j-issta2014} in our evaluation.
Table~\ref{tab:df4j} shows size, number of tests, and number of
faults, for each considered program. $2$ subjects from Math
were not considered because we were not able to reproduce them
in the machine used for the experiments.

@@

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\Fix{cite}\Sof{Not sure what to cite here}. A fault of omission occurs when
the program is buggy because some code is missing, i.e., a bug that is 
corrected by adding code. Intuitivelly, 
the ability of techniques to
produce good diagnosis in those cases reduce as \Fix{...explain...}. A
total of $59.7\%$ of the cases in this dataset manifest fault of
omission, which is a good indication of difficulty.

@@

%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
It is importance to notice that our study does not evaluate the fault of the \closure{} 
project since it requires high CPU to perform the \combpar{k} evaluation.
